\documentclass[landscape,twocolumn]{article}
\usepackage{amsmath, amssymb, biblatex, graphicx, hyperref, pgfplots, pgfplotstable}
\graphicspath{{../figures/}}
\addbibresource{references.bib}
\pgfplotsset{compat = 1.17}
%\pgfplotstableread[col sep=comma]{../results/results.csv}\results
\title{COMP5329 Assignment 2}
\author{John Hu (zehu4485, 500395897) \and Nicholas Grasevski (ngra5777, 500710654)}
\begin{document}
\maketitle
\begin{abstract}
In this report we implement a convolutional neural network for a multi-label image classification problem.
\end{abstract}

\section{Introduction}
\begin{itemize}
\item What's the aim of the study?
\item Why is the study important?
\item The general introduction of your used method in the assignment and your motivation for such a solution.
\end{itemize}

\section{Related work}
Existing related methods in the literature.

\section{Techniques}
\begin{itemize}
\item The principle of your method used in this assignment.
\item Justify the method.
\item Any advantage or novelty of the proposed method.
\end{itemize}

\section{Experiments}
\subsection{Performance}
\subsubsection{Accuracy}
\subsubsection{Efficiency}
\subsection{Analysis}
\subsubsection{Hyperparameters}
\subsubsection{Ablation studies}
\subsubsection{Comparison methods}

\section{Results}

\section{Discussion}

\section{Conclusion}

\printbibliography\appendix
\section{Running the code}
\begin{itemize}
\item Dependencies: \texttt{pip install torch}
\item Usage: \texttt{./assignment2.py}
\end{itemize}
The code assumes the data is stored in a directory called \texttt{input}.
\end{document}
